To whom it may concern,

I am excited to submit my application for the position of Software Engineer (PhD) Intern at \textbf{Cisco}. Currently I am employed as a Graduate Research Assistant at the Network Security lab of Virginia Tech under Dr. Taejoong Chung as a full-time Ph.D. student. My research is focused on how a data-driven approach can improve mismanagement and security of Email, HTTP, DNS, and public key infrastructure (PKI).

% As Cisco is one of the major players of Internet and networking, I believe an internship experience here will help me a great deal in increasing my domain expertise and giving me a sense of practicality in my research. I do fit the requirements mentioned in the job description as highlighted below and therefore, was greatly interested in an interview to know more about what do you work on and what can I bring to the table.  

As \textbf{NetApp} is one of the major players of \textbf{Cloud Networking Technology}, I believe an internship experience here will help me a great deal in increasing my domain expertise and giving me a sense of practicality in my research. I do fit the requirements mentioned in the job description as highlighted below and therefore, was greatly interested in an interview to know more about what do you work on and what can I bring to the table.

Here are some of my career highlights that may suit the requirements posted in your job requirements.

Proficient in Python, Java, JS, HTML, Linux, and experienced in Web development (front and back end) and API design

Advanced knowledge of Object-Oriented Programming, algorithms, data structures, operating system, computer architecture, network security, and relational DBMS

Strong teamwork skills demonstrated in collaborative research and team projects with multiple first-authored and co-authored publications in top security and measurement venues like USENIX Security, IMC, and PAM

Effective communication skills developed by interacting with students at different levels of expertise while being employed as a university lecturer and graduate teaching assistant

Have three open-source contributions in TextAttack, Mail-in-a-Box, and iRedAPD

Solid knowledge of networking protocols like TCP/IP and direct working knowledge of DNS, DNSSEC, HTTP, and email security extensions like SPF, DMARC, DANE, and MTA-STS etc.

I look forward to hearing more about the position and greatly appreciate your consideration.

Sincerely,
Mohammad Ishtiaq Ashiq Khan
iashiq5@vt.edu